The development of children's ability to track and predict turn structure in conversation

### 2015-12-17 paper/CasillasFrank-Anticip.tex
partial MCF pass

Participants looked at the screen most of the time during video playback (81\% and 91\% on average for children and adults, respectively). They primarily kept their eyes on the person who was currently speaking in both English and non-English videos: They gazed at the current speaker between 38\% and 63\% of the time, looking back at the addressee between 15\% and 20\% of the time (Table \ref{tab:e1_look}). Even three-year-olds looked more at the current speaker than anything else, whether the videos were in a language they could understand or not. Children looked at the current speaker less than adults did during the non-English videos. Despite this, their looks to the addressee did not increase substantially in the non-English videos, indicating that their looks away were probably related to boredom rather than confusion about ongoing turn structure. Overall, participants' pattern of gaze to current speakers demonstrated that they performed basic turn tracking during the videos, regardless of language. Figure \ref{fig:E1-randvsreal} shows participants' anticipatory gaze rates across age, language condition, and transition type, in the real data and the random baseline (described below).

@@

\begin{table}[h!]
\begin{small}
\begin{center}
  \begin{tabular}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                   & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)   &      -0.96146 &   0.84901 & -1.132 & 0.257446 \\    
    Age             &    -0.18268 &   0.17507 & -1.043 & 0.296725   \\  
    LgCond$=$\textit{non-English} &          -3.29347 &   0.96045 & -3.429 & 0.000606 *** \\
    Type$=$\textit{non-Question}          &     -1.10129 &   0.86494 & -1.273 & 0.202925     \\
    Duration      &       3.40169 &   1.22826 &  2.770 & 0.005614  **\\
    Age*LgCond$=$\textit{non-English} &       0.52065 &   0.21190 &  2.457 & 0.014008 ** \\  
    Age*TypeS$=$\textit{non-Question}          & -0.01628 &   0.19437 & -0.084 & 0.933232     \\
    LgCond$=$\textit{non-English}* &     2.68166 &   1.35016 &  1.986 & 0.047013 * \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*LgCond$=$\textit{non-English}* & -0.45632 &   0.30163 & -1.513 & 0.130315  \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)       &        -0.1966 &    0.6942 & -0.283 & 0.776988     \\
    LgCond$=$\textit{non-English}    &             -0.8812 &    0.9602 & -0.918 & 0.358754   \\  
    Type$=$\textit{non-Question}             &        -4.4953 &    1.3139 & -3.421 & 0.000623 *** \\
    Duration          &        -1.1227 &    1.9880 & -0.565 & 0.572238     \\
    LgCond$=$\textit{non-English}* &           3.2972 &    1.6101 &  2.048 & 0.040581 * \\ 
    Type$=$\textit{non-Question} &&&& \\
    LgCond$=$\textit{non-English}* &        1.3626 &    3.0077 &  0.453 & 0.650527     \\
    \hspace*{5mm} Duration &&&& \\
    Type$=$\textit{non-Question}*          &  10.5107 &    3.3459 &  3.141 & 0.001682  ** \\
    \hspace*{5mm} Duration &&&& \\
    LgCond$=$\textit{non-English}* & -6.3156 &    4.4926 & -1.406 & 0.159790 \\    
    Type$=$\textit{non-Question}* &&&& \\
    \hspace*{5mm} Duration &&&& \\
    \hline
  \end{tabular}
\end{center}
  \end{scriptsize}
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E1-models}
\end{table}

@@

\subsubsection{Participants}
We recruited 27 undergraduate adults and 129 children between ages 1;0--6;11 to participate in our experiment. We recruited our child participants from the Children's Discovery Museum in San Jose, California, targeting approximately 20 children for each of the six 1-year age groups (range$=$20--23). All participants were native English speakers, though some parents (N$=$27) reported that their child heard a second (and sometimes third) language at home. None of the adult participants reported fluency in a second language. We ran Experiment 2 at a local children's museum because it gave us access to children with a more diverse range of ages.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/FIG-EN-stim.png}
\end{center}
\caption{The six puppet pairs (and associated audio conditions). Each pair was linked to three distinct conversations from the same condition across the three experiment versions.}
\label{fig:puppets}
\end{figure}

@@

Participants' pattern of gaze indicated that they performed basic turn tracking across all ages and in all conditions. Participants again looked at the screen most of the time during video playback (82\% and 86\% average for children and adults, respectively), primarily looking at the person who was currently speaking (Table 2). They tracked the current speaker in every condition---even one-year-olds looked more at the current speaker than at anything else in the three limited cue conditions (40\% for \textit{words only}, 43\% for \textit{prosody only}, and 39\% for \textit{no speech}). There was a steady overall increase in looks to the current speaker with age and added linguistic information (Tables \ref{tab:look_e2} and \ref{tab:look_e2b}). Looks to the addressee also decreased with age, but the change was minimal. Figure \ref{fig:E2-randvsreal} shows participants' anticipatory gaze rates across age, the four language conditions, and transition type, in the real data and the random baseline.

\begin{table}[h]
\begin{center}
  \begin{tabular}{llcccc}
    \hline
    Age group & Speaker & Addressee & Other onscreen & Offscreen\\ 
    \hline
    1 & 0.44 & 0.14 & 0.23 & 0.19 \\ 
    2 & 0.50 & 0.13 & 0.24 & 0.14 \\ 
    3 & 0.47 & 0.12 & 0.25 & 0.16 \\ 
    4 & 0.48 & 0.11 & 0.29 & 0.12 \\ 
    5 & 0.54 & 0.11 & 0.20 & 0.14 \\ 
    6 & 0.60 & 0.12 & 0.18 & 0.10 \\
    Adult & 0.69 & 0.12 & 0.09 & 0.10 \\
%   Overall & 0.53 & 0.12 & 0.21 & 0.13 \\
    \hline
  \end{tabular}
\end{center}
  \caption{Average proportion of gaze to the current speaker and addressee during periods of talk across ages.}
\label{tab:look_e2}
\end{table}

\begin{table}[h]
\begin{center}
  \begin{tabular}{llcccc}
    \hline
    Condition & Speaker & Addressee & Other onscreen & Offscreen\\ 
    \hline
    Normal & 0.58 & 0.12 & 0.17 & 0.13 \\ 
    Words only & 0.54 & 0.11 & 0.24 & 0.10 \\ 
    Prosody only & 0.48 & 0.12 & 0.26 & 0.15 \\ 
    No speech & 0.44 & 0.13 & 0.26 & 0.18 \\
    \hline
  \end{tabular}
\end{center}
  \caption{Average proportion of gaze to the current speaker and addressee during periods of talk across conditions.}
\label{tab:look_e2b}
\end{table}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{figures/E2-samples-by-lang-groups-trans-types.png}
\end{center}
\caption{Anticipatory gaze rates across language condition and transition type for the real (blue, dark green, light green, and red) and randomly permuted baseline (gray). Vertical bars represent the standard error.} 
\label{fig:E2-randvsreal}
\end{figure}

\subsubsection{Statistical models}
\label{sec:models2}
We identified anticipatory gaze switches for all 85 usable turn transitions, and analyzed them for effects of language condition, transition type, and age with two mixed-effects logistic regressions. We again built separate models for children and adults because effects of age were only pertinent to the children's data. The child model included condition (normal/prosody only/words only/no speech; with no speech as the reference level), transition type (question vs. non-question), age (1, 2, 3, 4, 5, 6; numeric), and duration of the inter-turn gap (in seconds) as predictors, with full interactions between language condition, transition type, and age.  We again included the duration of the inter-turn gap as a control predictor and added random effects of item (turn transition) and participant, with random slopes of transition type for participants. The adult model included condition, transition type, their interactions, and duration as a control predictor, with participant and item included as random effects and random slopes of condition and transition type.

\begin{scriptsize}
\begin{longtable}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)                & -3.57414  &   0.48576 &  -7.358 & 1.87e-13 ***    \\
    Age                         & 0.02543 &    0.10260  &  0.248   & 0.8042        \\
    Type$=$\textit{non-Question}                      & -0.81873  &   0.59985 &  -1.365  &  0.1723        \\
    Duration                   &  4.17672  &   0.62446  &  6.689 & 2.25e-11 ***    \\
    Age*Type$=$\textit{non-Question}                &    0.15116   &  0.13643  &  1.108  &  0.2679        \\
	\hline
    Condition$=$\textit{normal}            &  0.36710 &    0.43296 &   0.848  &  0.3965        \\
    Age*Condition$=$\textit{normal}       &   0.12919 &    0.10227  &  1.263  &  0.2065        \\
    Condition$=$\textit{normal}*     &   0.91059  &   0.72095  &  1.263 &   0.2066        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}* &   -0.37542  &   0.16963  & -2.213 &   0.0269 *      \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}         &   -1.63429  &   0.86390 &  -1.892   & 0.0585 .      \\
    Age*Condition$=$\textit{prosody}       &   0.39317 &     0.18907 &   2.080  &  0.0376 *      \\
    Condition$=$\textit{prosody}*     &  1.77190  &   1.24864  &  1.419 &   0.1559        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{prosody}* &  -0.47057 &    0.28703 &  -1.639 &   0.1011        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}            &  -0.26741 &    0.59071 &  -0.453  &  0.6508        \\
    Age*Condition$=$\textit{words}           &   0.13740  &   0.13568   & 1.013  &  0.3112        \\
    Condition$=$\textit{words}*     &   -1.02193  &   1.01227  & -1.010  &  0.3127        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{words}*  &   0.08946  &   0.22349   & 0.400 &   0.6890        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\

    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)           &  -3.4557   &   0.7199 &  -4.800 & 1.58e-06 *** \\ 
    Type$=$\textit{non-Question}                  &   0.4292  &    0.6089  &  0.705 & 0.480916     \\ 
    Duration             &     4.7500   &   1.2480  &  3.806 & 0.000141 *** \\ 
	\hline
    Condition$=$\textit{normal}    &      1.2556   &   0.5633  &  2.229 & 0.025805 *   \\ 
    Condition$=$\textit{normal}* &   -0.9452  &    0.7631 &  -1.239 & 0.215475     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}     &     0.3349  &    0.8965  &  0.374 & 0.708692     \\ 
    Condition$=$\textit{prosody}*  &  0.6627  &    1.2138 &   0.546 & 0.585108     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}       &     1.5938  &    0.7208 &   2.211 & 0.027023 *   \\ 
    Condition$=$\textit{words}*   &  -1.1265  &    0.9109  & -1.237 & 0.216201     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
    &&&& \\
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{longtable}
\end{scriptsize}

@@

Using the same technique described in Experiment 1 (Section \ref{sec:randbaseline1}), we created and modeled 5,000 random permutations of participants' anticipatory gaze (see Figures \ref{fig:E2-ChiTs} and \ref{fig:E2-AduTs} for the full distributional data). Our baseline analyses revealed that none of the significant predictors from models of the original, turn-related data (Table \ref{tab:E2-models}: Children) can be explained by random looking. In the children's data, the original model's \textit{t}-values for language condition (\textit{prosody only}), gap duration, the two-way interaction of age and language condition (\textit{prosody only}) and the three-way interaction of age, transition type, and language condition (\textit{normal} speech) were all greater than 95\% of the randomly permuted \textit{t}-values (96.2\%, 100\%, 95.1\%, and 95.1\%, respectively). Similarly, the adults' data showed significant differentiation from the randomly permuted data for all originally significant predictors: gap duration and language condition for \textit{normal} speech and words-only speech (greater than 100\%, 96.8\%, and 98.7\% of random \textit{t}-values, respectively). The effects of language condition and transition type for the real and randomly permuted data can also be observed in Figure \ref{fig:E1-randvsreal}.

As before, we excluded the output of random-permutation models that resulted in convergence warnings in order to remove unreliable model estimates from our analyses (non-converging models made up 69\% and 70\% of models for children and adults, respectively; see the Supplementary Materials for more information on model exclusion).

\paragraph{Developmental effects}
The model of the children's data revealed two significant interactions with age, neither of which derived from random looking (Table \ref{tab:E2-models}; Figure \ref{fig:E2-randvsreal}). The first was a significant interaction of age and language condition (for \textit{prosody only} compared to the \textit{no speech} reference level), suggesting a different age effect between the two linguistic conditions. As in Experiment 1, we further explored each age interaction by extracting an average difference score over subjects for the effect of language condition (\textit{no speech} vs. \textit{prosody only}) within each random permutation of the data, making pairwise comparisons between the six age groups. These tests revealed that children's anticipation in the \textit{prosody only} condition significantly improved at ages five and six (difference scores greater than 95\% of the random data scores; \textit{p}$<$.05; see Figure \ref{fig:E2-lgageinteraction} for the full distributions).

The second age-based interaction was a three-way interaction of age, transition type, and language condition (for \textit{normal} speech compared to the \textit{no speech} baseline). We again created pairwise comparisons of the average difference scores for the transition type-language condition interaction across age groups in each random permutation of the data, finding that the effect of transition type in the \textit{normal} speech condition became larger with age, with significant improvements by age 4 over ages 1 and 2 (99.9\% and 98.86\%, respectively), by age 5 over age 4 (97.54\%), and by age 6 over ages 1, 2, and 5 (99.5\%, 97.36\%, and 95.04\%), all significantly different from chance (\textit{p}$<$.05; see Figure \ref{fig:E2-lgagetypeinteraction} for the full distributions).

Our main goal in extending the age range to 1- and 2-year-olds in Experiment 2 was to find the age of emergence for spontaneous turn structure predictions. As in Experiment 1, we used two-tailed \textit{t}-tests to compare children's real gaze rates to the random baseline in the \textit{normal} speech condition, in which the speech stimulus is most like what children hear every day. We tested real gaze rates against baseline for three age groups: ages one, two, and three. Two- and three-year-old children made anticipatory gaze switches significantly above chance both when all transitions were considered (2-year-olds: \textit{t}(26.193)$=$-4.137, \textit{p}$<$.001; 3-year-olds: \textit{t}(22.757)$=$-2.662, \textit{p}$<$.05) and for question transitions alone (2-year-olds: \textit{t}(25.345)$=$-4.269, \textit{p}$<$.001; 3-year-olds: \textit{t}(21.555)$=$-3.03, \textit{p}$<$.01). One-year-olds, however, made anticipatory gaze shifts that were only marginally above chance for turn transitions overall and for question turns alone (overall: \textit{t}(24.784)$=$-2.049, \textit{p}$=$.051; questions: \textit{t}(25.009)$=$-2.03, \textit{p}$=$.053).

\subsection{Discussion}
\label{sec:discussion2}
As in Experiment 1, children and adults spontaneously tracked the turn structure of the conversations, making anticipatory gaze switches at an above-chance rate across all ages, but not in all conditions (Table \ref{tab:look_e2}; Figure \ref{fig:E2-randvsreal}). However, when children had access to full linguistic information (in the \textit{normal} speech condition), they made more anticipatory gaze switches than expected by chance at age two (and even marginally at age one). Across conditions, children's anticipatory gaze rates were affected by gap duration, plus interactions of language condition, transition type and age (Table \ref{tab:E2-models}), none of which could be explained by a baseline of random gaze switching (Figure \ref{fig:E2-ChiTs}).

Two of the three linguistic conditions affected children's anticipatory gaze switches, compared to the no-speech reference level: prosody-only speech and \textit{normal} speech. \textit{Prosody only} speech resulted in fewer anticipatory gazes overall, compared to the no-speech baseline, though the effect was only marginal (\textit{p}$=$.06). However, prosody-only speech \textit{did} significantly differ from the \textit{no speech} condition in its interaction with age: Whereas age gains were negligible in the \textit{no speech} condition, 5- and 6-year-olds in the prosody-only condition showed significantly more anticipatory gaze switches than younger children (Figure \ref{fig:E2-lgageinteraction}), going from at-chance anticipatory gaze rates to rates well above chance (Figure \ref{fig:E2-randvsreal}).

Anticipatory gaze for questions increased significantly more with age in the \textit{normal} speech condition compared to the no-speech baseline. As in Experiment 1, children consistently made more anticipatory gazes after hearing questions when they had access to lexical material. But now, with a larger age span in Experiment 2, we can begin to see a developmental path for the question effect. At least for \textit{normal} speech, greater anticipatory looking for questions is not present from the start: 4-year-olds are the first to make significant gains on 1- and 2-year-olds, but then there are further significant gains at age 5, and again age 6 (Figure \ref{fig:E2-lgagetypeinteraction}). While children at ages five and six showed adult-like differentiation of questions and non-questions in the \textit{normal} speech condition, 1-year-olds had nearly identical switch rates for the two transition types. This suggests that the participants' tendency to make more anticipatory switches for questions emerges after age one and continues developing, with rapid gains in ages three through age six. Finally, children showed a straightforward effect of gap duration (Table \ref{tab:E2-models}), as in Experiment 1.

Adults' anticipatory gaze rates were affected by gap duration and two of the language conditions (Table \ref{tab:E2-models}), none of which could be explained by a baseline of random gaze switching (Figure \ref{fig:E2-AduTs}). Adults made more anticipatory switches overall for the \textit{normal} speech and words-only conditions compared to the no-speech condition, falling in-line with past work showing that adults primarily use lexical information in making predictions about upcoming turn structure \citep{de-ruiter2006}. Though adults did make more anticipatory switches for questions than non-questions on average in the two lexical conditions (Figure \ref{fig:E2-randvsreal}), the effect of transition type was not significant in either one (Table \ref{tab:E2-models}). Like children, adults also showed a straightforward effect of gap duration.

>>>>

Participants looked at the screen most of the time during video playback (81\% and 91\% on average for children and adults, respectively). They primarily kept their eyes on the person who was currently speaking in both English and non-English videos: They gazed at the current speaker between 38\% and 63\% of the time, looking back at the addressee between 15\% and 20\% of the time (Table \ref{tab:e1_look}). Even three-year-olds looked more at the current speaker than anything else, whether the videos were in a language they could understand or not. Children looked at the current speaker less than adults did during the non-English videos. Despite this, their looks to the addressee did not increase substantially in the non-English videos, indicating that their looks away were probably related to boredom rather than confusion about ongoing turn structure. Overall, participants' pattern of gaze to current speakers demonstrated that they performed basic turn tracking during the videos, regardless of language. Figure \ref{fig:E1-randvsreal} shows participants' anticipatory gaze rates across age, language condition, and transition type.

@@

\begin{table}[h!]
\begin{small}
\begin{center}
  \begin{tabular}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                   & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)   &      -0.96146 &   0.84901 & -1.132 & 0.257446 \\    
    Age             &    -0.18268 &   0.17507 & -1.043 & 0.296725   \\  
    LgCond$=$\textit{non-English} &          -3.29347 &   0.96045 & -3.429 & 0.000606 *** \\
    Type$=$\textit{non-Question}          &     -1.10129 &   0.86494 & -1.273 & 0.202925     \\
    Duration      &       3.40169 &   1.22826 &  2.770 & 0.005614  **\\
    Age*LgCond$=$\textit{non-English} &       0.52065 &   0.21190 &  2.457 & 0.014008 ** \\  
    Age*TypeS$=$\textit{non-Question}          & -0.01628 &   0.19437 & -0.084 & 0.933232     \\
    LgCond$=$\textit{non-English}* &     2.68166 &   1.35016 &  1.986 & 0.047013 * \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*LgCond$=$\textit{non-English}* & -0.45632 &   0.30163 & -1.513 & 0.130315  \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)       &        -0.1966 &    0.6942 & -0.283 & 0.776988     \\
    LgCond$=$\textit{non-English}    &             -0.8812 &    0.9602 & -0.918 & 0.358754   \\  
    Type$=$\textit{non-Question}             &        -4.4953 &    1.3139 & -3.421 & 0.000623 *** \\
    Duration          &        -1.1227 &    1.9880 & -0.565 & 0.572238     \\
    LgCond$=$\textit{non-English}* &           3.2972 &    1.6101 &  2.048 & 0.040581 * \\ 
    Type$=$\textit{non-Question} &&&& \\
    LgCond$=$\textit{non-English}* &        1.3626 &    3.0077 &  0.453 & 0.650527     \\
    \hspace*{5mm} Duration &&&& \\
    Type$=$\textit{non-Question}*          &  10.5107 &    3.3459 &  3.141 & 0.001682  ** \\
    \hspace*{5mm} Duration &&&& \\
    LgCond$=$\textit{non-English}* & -6.3156 &    4.4926 & -1.406 & 0.159790 \\    
    Type$=$\textit{non-Question}* &&&& \\
    \hspace*{5mm} Duration &&&& \\
    \hline
  \end{tabular}
\end{center}
  \end{small}
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E1-models}
\end{table}

@@

\subsubsection{Participants}
We recruited 27 undergraduate adults and 129 children between ages 1;0--6;11 to participate in our experiment. We recruited our child participants from Children's Discovery Museum of San Jose, California, targeting approximately 20 children for each of the six one-year age groups (range: 20--23). All participants were native English speakers, though some parents (N$=$27) reported that their child heard a second (and sometimes third) language at home. None of the adult participants reported fluency in a second language. We ran Experiment 2 at a local children's museum because it gave us access to children with a more diverse range of ages.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{figures/FIG-EN-stim.png}
\end{center}
\caption{The six puppet pairs (and associated audio conditions). Each pair was linked to three distinct conversations from the same condition across the three experiment versions.}
\label{fig:puppets}
\end{figure}

@@

Participants' pattern of gaze indicated that they performed basic turn tracking across all ages and in all conditions. Participants again looked at the screen most of the time during video playback (82\% and 86\% average for children and adults, respectively), primarily looking at the person who was currently speaking (Table 2). They tracked the current speaker in every condition---even one-year-olds looked more at the current speaker than at anything else in the three limited cue conditions (40\% for \textit{words only}, 43\% for \textit{prosody only}, and 39\% for \textit{no speech}). There was a steady overall increase in looks to the current speaker with age and added linguistic information (Tables \ref{tab:look_e2} and \ref{tab:look_e2b}). Looks to the addressee also decreased with age, but the change was minimal. Figure \ref{fig:E2-randvsreal} shows participants' anticipatory gaze rates across age, the four language conditions, and transition type.

\begin{table}[t]
\begin{center}
  \begin{tabular}{llcccc}
    \hline
    Age group & Speaker & Addressee & Other onscreen & Offscreen\\ 
    \hline
    1 & 0.44 & 0.14 & 0.23 & 0.19 \\ 
    2 & 0.50 & 0.13 & 0.24 & 0.14 \\ 
    3 & 0.47 & 0.12 & 0.25 & 0.16 \\ 
    4 & 0.48 & 0.11 & 0.29 & 0.12 \\ 
    5 & 0.54 & 0.11 & 0.20 & 0.14 \\ 
    6 & 0.60 & 0.12 & 0.18 & 0.10 \\
    Adult & 0.69 & 0.12 & 0.09 & 0.10 \\
%   Overall & 0.53 & 0.12 & 0.21 & 0.13 \\
    \hline
  \end{tabular}
\end{center}
  \caption{Average proportion of gaze to the current speaker and addressee during periods of talk across ages.}
\label{tab:look_e2}
\end{table}

\begin{table}[t]
\begin{center}
  \begin{tabular}{llcccc}
    \hline
    Condition & Speaker & Addressee & Other onscreen & Offscreen\\ 
    \hline
    Normal & 0.58 & 0.12 & 0.17 & 0.13 \\ 
    Words only & 0.54 & 0.11 & 0.24 & 0.10 \\ 
    Prosody only & 0.48 & 0.12 & 0.26 & 0.15 \\ 
    No speech & 0.44 & 0.13 & 0.26 & 0.18 \\
    \hline
  \end{tabular}
\end{center}
  \caption{Average proportion of gaze to the current speaker and addressee during periods of talk across conditions.}
\label{tab:look_e2b}
\end{table}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{figures/E2-samples-by-lang-groups-trans-types_mod.png}
\end{center}
\caption{Anticipatory gaze rates across language condition and transition type for the real (blue, dark green, light green, and red) and randomly permuted baseline (gray). Vertical bars represent the standard error.} 
\label{fig:E2-randvsreal}
\end{figure}

\subsubsection{Statistical models}
\label{sec:models2}

We identified anticipatory gaze switches for all 85 usable turn transitions, and analyzed them for effects of language condition, transition type, and age with two mixed-effects logistic regressions. We again built separate models for children and adults because effects of age were only pertinent to the children's data. The child model included condition (normal/prosody only/words only/no speech; with no speech as the reference level), transition type (question vs. non-question), age (1, 2, 3, 4, 5, 6; numeric), and duration of the inter-turn gap (in seconds) as predictors, with full interactions between language condition, transition type, and age.  We again included the duration of the inter-turn gap as a control predictor and added random effects of item (turn transition) and participant, with random slopes of transition type for participants. The adult model included condition, transition type, their interactions, and duration as a control predictor, with participant and item included as random effects and random slopes of condition and transition type.

\begin{footnotesize}
\begin{longtable}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)                & -3.57414  &   0.48576 &  -7.358 & 1.87e-13 ***    \\
    Age                         & 0.02543 &    0.10260  &  0.248   & 0.8042        \\
    Type$=$\textit{non-Question}                      & -0.81873  &   0.59985 &  -1.365  &  0.1723        \\
    Duration                   &  4.17672  &   0.62446  &  6.689 & 2.25e-11 ***    \\
    Age*Type$=$\textit{non-Question}                &    0.15116   &  0.13643  &  1.108  &  0.2679        \\
	\hline
    Condition$=$\textit{normal}            &  0.36710 &    0.43296 &   0.848  &  0.3965        \\
    Age*Condition$=$\textit{normal}       &   0.12919 &    0.10227  &  1.263  &  0.2065        \\
    Condition$=$\textit{normal}*     &   0.91059  &   0.72095  &  1.263 &   0.2066        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}* &   -0.37542  &   0.16963  & -2.213 &   0.0269 *      \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}         &   -1.63429  &   0.86390 &  -1.892   & 0.0585 .      \\
    Age*Condition$=$\textit{prosody}       &   0.39317 &     0.18907 &   2.080  &  0.0376 *      \\
    Condition$=$\textit{prosody}*     &  1.77190  &   1.24864  &  1.419 &   0.1559        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{prosody}* &  -0.47057 &    0.28703 &  -1.639 &   0.1011        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}            &  -0.26741 &    0.59071 &  -0.453  &  0.6508        \\
    Age*Condition$=$\textit{words}           &   0.13740  &   0.13568   & 1.013  &  0.3112        \\
    Condition$=$\textit{words}*     &   -1.02193  &   1.01227  & -1.010  &  0.3127        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{words}*  &   0.08946  &   0.22349   & 0.400 &   0.6890        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\

    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)           &  -3.4557   &   0.7199 &  -4.800 & 1.58e-06 *** \\ 
    Type$=$\textit{non-Question}                  &   0.4292  &    0.6089  &  0.705 & 0.480916     \\ 
    Duration             &     4.7500   &   1.2480  &  3.806 & 0.000141 *** \\ 
	\hline
    Condition$=$\textit{normal}    &      1.2556   &   0.5633  &  2.229 & 0.025805 *   \\ 
    Condition$=$\textit{normal}* &   -0.9452  &    0.7631 &  -1.239 & 0.215475     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}     &     0.3349  &    0.8965  &  0.374 & 0.708692     \\ 
    Condition$=$\textit{prosody}*  &  0.6627  &    1.2138 &   0.546 & 0.585108     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}       &     1.5938  &    0.7208 &   2.211 & 0.027023 *   \\ 
    Condition$=$\textit{words}*   &  -1.1265  &    0.9109  & -1.237 & 0.216201     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
    &&&& \\
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{longtable}
\end{footnotesize}

@@

Using the same technique described in Experiment 1 (Section \ref{sec:randbaseline1}), we created and modeled random permutations of participants' anticipatory gaze. These analyses revealed that none of the significant predictors from models of the original, turn-related data could be explained by random looking. In the children's data, the original model's \textit{t}-values for language condition (\textit{prosody only}), gap duration, the two-way interaction of age and language condition (\textit{prosody only}) and the three-way interaction of age, transition type, and language condition (\textit{normal} speech) were all greater than 95\% of the randomly permuted \textit{t}-values (96.2\%, 100\%, 95.1\%, and 95.1\%, respectively). Similarly, the adults' data showed significant differentiation from the randomly permuted data for all originally significant predictors: gap duration and language condition for \textit{normal} speech and words-only speech (greater than 100\%, 96.8\%, and 98.7\% of random \textit{t}-values, respectively). 
% The effects of language condition and transition type for the real and randomly permuted data can also be observed in Figure \ref{fig:E1-randvsreal}.

Our main goal in extending the age range to 1- and 2-year-olds in Experiment 2 was to find the age of emergence for spontaneous turn structure predictions in our paradigm. As in Experiment 1, we used two-tailed \textit{t}-tests to compare children's real gaze rates to the random baseline in the \textit{normal} speech condition, in which the speech stimulus is most like what children hear every day. We tested real gaze rates against baseline for three age groups: ages one, two, and three. Two- and three-year-old children made anticipatory gaze switches significantly above chance both when all transitions were considered (2-year-olds: \textit{t}(26.193)$=$-4.137, \textit{p}$<$.001; 3-year-olds: \textit{t}(22.757)$=$-2.662, \textit{p}$<$.05) and for question transitions alone (2-year-olds: \textit{t}(25.345)$=$-4.269, \textit{p}$<$.001; 3-year-olds: \textit{t}(21.555)$=$-3.03, \textit{p}$<$.01). One-year-olds, however, made anticipatory gaze shifts that were not statistically significant for turn transitions overall and for question turns alone (overall: \textit{t}(24.784)$=$-2.049, \textit{p}$=$.051; questions: \textit{t}(25.009)$=$-2.03, \textit{p}$=$.053).

Regression models for the children's data also revealed two significant interactions with age. The first was a significant interaction of age and language condition (for \textit{prosody only} compared to the \textit{no speech} reference level), suggesting a different age effect between the two linguistic conditions. As in Experiment 1, we further explored each age interaction by extracting an average difference score over subjects for the effect of language condition (\textit{no speech} vs. \textit{prosody only}) within each random permutation of the data, making pairwise comparisons between the six age groups. These tests revealed that children's anticipation in the \textit{prosody only} condition significantly improved at ages five and six (difference scores greater than 95\% of the random data scores (\textit{p}$<$.05).

The second age-based interaction was a three-way interaction of age, transition type, and language condition (for \textit{normal} speech compared to the \textit{no speech} baseline). We again created pairwise comparisons of the average difference scores for the transition type-language condition interaction across age groups in each random permutation of the data, finding that the effect of transition type in the \textit{normal} speech condition became larger with age, with significant improvements by age 4 over ages 1 and 2 (99.9\% and 98.86\%, respectively), by age 5 over age 4 (97.54\%), and by age 6 over ages 1, 2, and 5 (99.5\%, 97.36\%, and 95.04\%), all significantly different from chance (\textit{p}$<$.05).

\subsection{Discussion}
\label{sec:discussion2}

The core aims of Experiment 2 were to gain better traction on the individual roles of prosody and lexicosyntax in children's turn predictions, and to find the age of emergence for spontaneous turn anticipation. Taken together, our results replicate the findings from Experiment 1: Participants make more anticipatory switches when they have access to lexical information and, when they do, tend to make more anticipatory switches for questions compared to non-questions.

As in Experiment 1, with normal speech, children and adults spontaneously tracked the turn structure of the conversations, making anticipatory gaze switches at an above-chance rate across all ages. And in addition, they made far more anticipations for questions than for non-question turns---at least for two-year-olds and older. But these effects were different for the two comparison conditions, \textit{prosody-only} and \textit{words-only}. In the \textit{prosody-only} condition, performance was low for younger children and increased substantially for older children (especially for questions). In the \textit{words-only} condition, anticipation performance was relatively robust for questions for two-year-olds and older (much like in normal speech), but never rose above chance for the children for non-question turns. Thus, these findings do not support an early role for prosody in children's spontaneous turn structure predictions. On the contrary, children's predictions appeared to stem more from lexical information, probably primarily from question words.
